### 2017-01-04 paper/evaluation.tex
Fixed subsection label
rephrased RQ
fixed typo

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
regression test suites in open-source projects?}
\newcommand{\RQB}{How the time cost from a test suite is distributed
among the test cases?}
\newcommand{\RQC}{How often are parallelization features in
build files?}
\newcommand{\RQD}{What is the impact of parallelization?}
\newcommand{\RQE}{What factors contribute to improve performance
through parallelization?\Jbc{Previously as "When does parallelization
works and when it does not so great?"}}
\newcommand{\RQF}{What are the limitations of parallelization?}

@@

\subsection{Answering research question RQ1}
\label{sec:rqone}

@@

To evaluate the presence of parallelization settings, we considered
the \numSubjsRqTwo{} subjects from the groups \emph{long} and
\emph{medium} identified in Section~\ref{sec:rqA}. We focused on
these two groups because given that costly test suites exist, we
wanted to analyze if their maintainers are aware of parallelization
settings and how they use these settings.  We computed the
frequency of the parallelism modes (see Section \ref{sec:modes}) using
a semi-automatic approach: we first discover automatically the
relevant build files (\ie, \emph{pom.xml} files) and then we manually
inspect them to eliminate false-positves (\eg, commented
configuration).  Figure~\ref{fig:discovery-step} describes the
discovery step: first, we list the paths of all build file and then we
filter only the build files that contain any of the keywords,
\CodeIn{forkMode}, \CodeIn{forkCount}, or \CodeIn{parallel}. Notice
that, for Maven projects, any of these keywords exist in any possible
parallelism configuration \Fix{cite surefire doc}.

>>>>

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
regression test suites in open-source projects?}
\newcommand{\RQB}{How the time cost from a test suite is distributed
among the test cases?}
\newcommand{\RQC}{How often parallelization features appear in
build files?}
\newcommand{\RQD}{What is the impact of parallelization?}
\newcommand{\RQE}{What factors contribute to improve performance
through parallelization?\Jbc{Previously as "When does parallelization
works and when it does not so great?"}}
\newcommand{\RQF}{What are the limitations of parallelization?}

@@

\subsection{Answering research question RQ1}
\label{sec:rqA}

@@

To evaluate the presence of parallelization settings, we considered
the \numSubjsRqTwo{} subjects from the groups \emph{long} and
\emph{medium} identified in Section~\ref{sec:rqA}. We focused on
these two groups because given that costly test suites exist, we
wanted to analyze if their maintainers are aware of parallelization
settings and how they use these settings.  We computed the
frequency of the parallelism modes (see Section \ref{sec:modes}) using
a semi-automatic approach: we first discover automatically the
relevant build files (\ie, \emph{pom.xml} files) and then we manually
inspect them to eliminate false-positives (\eg, commented
configuration).  Figure~\ref{fig:discovery-step} describes the
discovery step: first, we list the paths of all build file and then we
filter only the build files that contain any of the keywords,
\CodeIn{forkMode}, \CodeIn{forkCount}, or \CodeIn{parallel}. Notice
that, for Maven projects, any of these keywords exist in any possible
parallelism configuration \Fix{cite surefire doc}.
